\textbf{\sc Towards Deliberative Control in Marine Robotics}

### 2012-04-25 concepts.tex
updates to review

\eu uses a \emph{state variable} representation
\cite{mus94,jonsson00,mcgann09} to describe the evolution of state
over time. The instantiated history of such state variable evolution
over a temporal horizon we call \emph{timelines} and which represent a
single thread in the execution of a concurrent system. At any given
time each thread can execute a single procedure.  Thus each timeline
consists of a sequence of procedures which encapsulate and describe
state evolution; we call these instantiated atomic entities
\emph{tokens}.  A token therefore describes a procedure invocation,
the state variables on which it can occur, the parameter values of the
procedure, and the time values defining the interval. We allow
encapsulation of uncertainty within these tokens with a range of start
and end times and parameters, all of which are encoded as variables. A
constraint solver in turn manipulates these variables defined in a \eu
domain model. For example, consider a scientific need to take water
samples 100 meters from an environmental hotspot while an AUV is
performing a Yo-Yo sawtooth pattern\footnote{\kcomment{Variability in
    the water column is along the vertical dimension. Since the Dorado
    platform can only move forward, the Yo-Yo pattern is the most
    efficient mechanism for studying water column properties.}}  in
the water-column. Two samples are needed if the feature's signal is
above a threshold; one otherwise. The token that is capturing the
sensory threshold has a parametric constraints to the token which
fires the requisite water sampler. In addition, the start time of the
water sampling procedure is highly dependant on the variability of
sub-sea currents and actual speed of the vehicle. Therefore a number
of values are possible for the start times and duration of the
sampling all of which are valid combinations for desired outcomes.

@@

\item[\textbf{Objects}] The items we wish to describe and refer to in
  a domain are considered objects. As in the case with object-oriented
  analysis and design, one can seek out the nouns in any domain
  description to find likely objects. In the Shopping Agent example,
  we might consider the Agent, Products and Locations all to be
  objects. Objects have state and behavior, for example, a Shopping
  Agent can have, its location, a bag that contains the products it
  has already purchased (the bag can in turn be another object) and
  behavior as in going to a location to look for a product, perform a
  purchase, return home, etc.

  Objects that have similar state and behavior can be described
  generically in terms of object types or classes. \eu allows the
  definition of classes similar to object-oriented programming
  languages, where a class can have attributes (represented by
  variables), and classes can be arranged in a single-parent hierarchy
  through inheritance.  However, one key aspect in \eu that is not
  found in object-oriented programming: to describe state and behavior
  for the purposes of planning we need to build on the formalism of
  first order logic.

@@

\item[\textbf{Rules}] In order for a plan to be valid, it must comply
  with all rules pertinent to the relevant application domain. Rules
  govern the internal and external relationships of a token. For
  example, consider a parameterized action
  \texttt{Go(origin,destination)} which describes a Shopping Agent
  traveling from one location (\textit{origin}) to another
  (\textit{destination}). The parameters are instantiated on a token
  as variables whose domain of values is the set of all possible
  locations in a given problem. A rule governing an internal
  relationship among token variables might stipulate that a transition
  must involve a change in location. This can be expressed as a
  constraint on the definition of a predicate of the form:
  \textit{origin != destination}. A further stipulation could be that
  the agent must be located at \textit{origin} before travel can occur
  and the agent must be located at \textit{destination} when travel is
  completed. This is an example of a rule governing an external
  relationship among tokens. It specifies a requirement that tokens of
  the predicate \texttt{At} that represent the location state for the
  Shopping Agent precede and succeed tokens of the predicate
  \texttt{Go} that represents traveling. Fig. \ref{fig:europapr:rules}
  illustrates the entities and relations involved in specifying such a
  rule on a \texttt{Go} action. The token on which the rule applies
  (\texttt{Go}) is referred to as the \emph{master}. Each \texttt{At}
  and \texttt{Going} token required by the master is referred to as a
  \emph{slave}.  Application of a rule on a token can thus cause slave
  tokens, variables and constraints to be introduced.  The capability
  of a domain rule to cause a slave token to be created is a key
  vehicle through which planning occurs. Semantically, a rule imposes
  a requirement for supporting (slave) tokens to be in the plan in
  order for the master token to be valid.

  \begin{figure}[t]
    \centering
    \includegraphics[scale=0.4]{figs/europa-pr-rules.pdf}
    \caption{\small Master and Slave tokens generated as a result of a domain rule.}
    \label{fig:europapr:rules}
  \end{figure}

>>>>

\eu uses a \emph{state variable} representation
\cite{mus94,jonsson00,py10} to describe the evolution of state over
time. The instantiated history of such state variable evolution over a
temporal horizon we call \kcomment{as a} \emph{timeline} and
\kcomment{one which represents} a single thread in the execution of a
concurrent system. At any given time each thread can execute a single
procedure.  Thus each timeline consists of a sequence of procedures
which encapsulate and describe state evolution; we call these
instantiated atomic entities \emph{tokens}.  A token therefore
describes a procedure invocation, the state variables on which it can
occur, the parameter values of the procedure, and the time values
defining the interval. We allow encapsulation of uncertainty within
these tokens with a range of start and end times and parameters, all
of which are encoded as variables. A constraint solver in turn
manipulates these variables defined in a \eu domain model. For
example, consider a scientific need to take water samples 100 meters
from an environmental hotspot while an AUV is performing a Yo-Yo
sawtooth pattern\footnote{\kcomment{Variability in the water column is
    along the vertical dimension. Since the Dorado platform can only
    move forward, the Yo-Yo pattern is the most efficient mechanism
    for studying water column properties.}}  in the water-column. Two
samples are needed if the feature's signal is above a threshold; one
otherwise. The token that is capturing the sensory threshold has a
parametric constraints to the token which fires the requisite water
sampler. In addition, the start time of the water sampling procedure
is highly dependant on the variability of sub-sea currents and actual
speed of the vehicle. Therefore a number of values are possible for
the start times and duration of the sampling all of which are valid
combinations for desired outcomes.

@@

\item[\textbf{Objects}] The items we wish to describe and refer to in
  a domain are considered objects. % As in the case with object-oriented
  % analysis and design, one can seek out the nouns in any domain
  % description to find likely objects. ---- this seemed confusing
  In the Shopping Agent example, we might consider the Agent, Products
  and Locations all to be objects. Objects have state and behavior.
  For example, a Shopping Agent can have its location, a bag that
  contains the products it has already purchased (the bag can in turn
  be another object) and behavior, as in going to a location to look
  for a product, perform a purchase, return home, etc. all as objects.
  Those that have similar state and behavior can be described
  generically in terms of object types or classes. \eu allows the
  definition of classes similar to object-oriented programming
  languages, where a class can have attributes (represented by
  variables) and classes can be arranged in a single-parent hierarchy
  through inheritance.  \kcomment{What is different however, is that
    to describe state and behavior for planning one needs} to build on
  the formalism of first order logic.

@@

\item[\textbf{Rules}] In order for a plan to be valid, it must comply
  with all rules pertinent to the relevant application domain. Rules
  govern the internal and external relationships of a token. For
  example, consider a parameterized action
  \texttt{Go(origin,destination)} which describes a Shopping Agent
  traveling from one location (\textit{origin}) to another
  (\textit{destination}). The parameters are instantiated on a token
  as variables whose domain of values is the set of all possible
  locations in a given problem. A rule governing an internal
  relationship among token variables might stipulate that a transition
  must involve a change in location. This can be expressed as a
  constraint on the definition of a predicate of the form:
  \textit{origin != destination}. A further stipulation could be that
  the agent must be located at \textit{origin} before travel can occur
  and the agent must be located at \textit{destination} when travel is
  completed. This is an example of a rule governing an external
  relationship among tokens. It specifies a requirement that tokens of
  the predicate \texttt{At} that represent the location state for the
  Shopping Agent precede and succeed tokens of the predicate
  \texttt{Go} that represents traveling. Fig. \ref{fig:europapr:rules}
  illustrates the entities and relations involved in specifying such a
  rule on a \texttt{Go} action. The token on which the rule applies
  (\texttt{Go}) is referred to as the \emph{master}. Each \texttt{At}
  and \texttt{Going} token required by the master is referred to as a
  \emph{slave}.  Application of a rule on a token \kcomment{(\ie a
    master)} can thus cause slave tokens, variables and constraints to
  be introduced.  The capability of a domain rule to cause a slave
  token to be created is a key vehicle through which planning
  occurs. Semantically, a rule imposes a requirement for supporting
  slave tokens to be in the plan in order for the master token to be
  valid.

  \begin{figure}[t]
    \centering
    \includegraphics[scale=0.45]{figs/europa-pr-rules.pdf}
    \caption{\small Master and Slave tokens generated as a result of a domain rule.}
    \label{fig:europapr:rules}
  \end{figure}
